---
output: html_document
---
# Data Wrangling Exercise 1: Basic Data Manipulation
Author: Eliza J. Villarino

This contains the codes I've created for Data Wrangling Exercise 1: Basic Data Manipulation for Springboard's Data Science Workshop.

### Load the data in RStudio

``` {r}
refine_original <- read.csv("C:/Users/elizajv/Documents/Data science exercises/refine.csv", 1)
View(refine_original)
as.data.frame(refine_original)
```

### Clean up brand names

Standardize spelling of company names as "philips", "akzo", "van houten" and "unilever

``` {r}
refine_original$company[refine_original$company=="Phillips"] <- "philips"
refine_original$company[refine_original$company=="philips"] <- "philips"
refine_original$company[refine_original$company=="phllips"] <- "philips"
refine_original$company[refine_original$company=="phillps"] <- "philips"
refine_original$company[refine_original$company=="phillipS"] <- "philips"
refine_original$company[refine_original$company=="fillips"] <- "philips"
refine_original$company[refine_original$company=="phlips"] <- "philips"
refine_original$company[refine_original$company=="Akzo"] <- "akzo"
refine_original$company[refine_original$company=="akz0"] <- "akzo"
refine_original$company[refine_original$company=="ak zo"] <- "akzo"
refine_original$company[refine_original$company=="AKZO"] <- "akzo"
refine_original$company[refine_original$company=="Van Houten"] <- "van houten"
refine_original$company[refine_original$company=="van Houten"] <- "van houten"
refine_original$company[refine_original$company=="unilver"] <- "unilever"
refine_original$company[refine_original$company=="Unilever"] <- "unilever"
```

### Separate product code and number

Split *Product.code...number* into *product_code* and *product_number*, respectively; add *product_code* and *product_number* to the dataframe

```{r}
refine_original$Product.code...number <- as.character(refine_original$Product.code...number)
product_code_number_split <- strsplit(refine_original$Product.code...number, split = "-")
select_el <- function(x, index) {x[index]}
product_code <- lapply(product_code_number_split, select_el, index = 1) 
product_number <- lapply(product_code_number_split, select_el, index = 2) 
refine_original$product_code <- as.character(product_code)
refine_original$product_number <- as.numeric(product_number)
```

### Add product categories

Create the variable *product_category* with observations "Smartphone", "TV", "Laptop" and "Tablet" as equivalent to "p", "v", "x" and "q" in the product_code column

```{r}
y <- refine_original$product_code
x <- c("Smartphone", "TV", "Laptop", "Tablet")
refine_original$product_category <- ifelse(y == "p", x[1], ifelse(y == "v", x[2], ifelse(y == "x", x[3], ifelse(y == "q", x[4], NA))))
```

### Add full address for geocoding

Concatenate *full_address* with variables "address", "city" and "country" separated by commas then add *full_address* to the dataframe

```{r}
full_address <- as.character(paste(refine_original$address, refine_original$city, refine_original$country, sep = ","))
refine_original$full_address <- full_address
```

### Create dummy variables for company and product category

Create binary variables for company names and product categories and add them to the dataframe

``` {r}
refine_original$company_philips <- as.numeric(refine_original$company == "philips")
refine_original$company_akzo <- as.numeric(refine_original$company == "akzo")
refine_original$company_van_houten <- as.numeric(refine_original$company == "van houten")
refine_original$company_unilever <- as.numeric(refine_original$company == "unilever")
refine_original$product_smartphone <- as.numeric(refine_original$product_category == "Smartphone")
refine_original$product_tv <- as.numeric(refine_original$product_category == "TV")
refine_original$product_laptop <- as.numeric(refine_original$product_category == "Laptop")
refine_original$product_tablet <- as.numeric(refine_original$product_category == "Tablet")
```

### Save cleaned data 

``` {r}
refine_clean <- refine_original
write.csv(refine_clean, "refine_clean.csv")
```
