## Data Wrangling Exercise 2: Dealing with missing values
Author: Eliza J. Villarino

This accomplishes the Data Wrangling Exercise 2: Dealing with missing values.

### Load dataset

Download and save the *titanic* dataset as *titanic_original.csv*. Load the *titanic_original* dataset.

``` {r}
titanic_original <- read.csv("C:/Users/elizajv/Documents/Data science exercises/titanic3.csv")

library(tidyr)
library(plyr)
library(dplyr)
```

### Find and replace missing values in the *embarked* column

Find the missing values in the *embarked* column and replace them with "S".

```{r}
titanic_original$embarked[titanic_original$embarked == ''] <- "S"
```

### Replace missing values in *age* column with the mean of all complete values


```{r}
titanic_original$age <- titanic_original %>% select(age) %>%
  replace_na(list(age=mean(titanic_original$age, na.rm=T)))
```

### Fill empty slots in *boat* column with NA

```{r}
titanic_original$boat[titanic_original$boat == ''] <- NA
```

### Create *has_cabin_number* column

Create *has_cabin_number* column with values 1 for complete cases and 0 for missing values in the *cabin* column.

```{r}
titanic_original$has_cabin_number <- ifelse(titanic_original$cabin=="", 0, 1)
```

### Save the cleaned data

``` {r}
titanic_clean <- titanic_original
write.csv(titanic_clean, "titanic_clean.csv")
```
